\documentclass{letter}
\signature{Benjamin Schroeder \\
				 Graduate Research Assistant \\ 
				 University of Utah \\
				 Chemical Engineering \\
  				 benjamin.schroeder@utah.edu}
\address{University of Utah \\ 
				The Institute for Clean and Secure Energy \\ 
				155 South 1452 East, INSCC 350 \\ 
				Salt Lake City UT, 84112}

\begin{document}
\begin{letter} {Dr. Marc Norman \\
					   Executive Editor \\ 
					   Geochimica et Cosmochimica Acta}

\opening{Dear Dr. Marc Norman:}
We appreciate your time and consideration regarding our article: ``a theoretical framework for multiple-polymorph precipitation of calcium carbonate".  I (Benjamin Schroeder) will be acting as the corresponding author for this article and my coauthors include Derek Harris, a graduate student at Brigham Young University, Dr. Sean Smith, a research assistant professor at the University of Utah, and Dr. David Lignell, an assistant professor at Brigham Young University.  The submitted article is an original piece of work that has not been submitted elsewhere and the coauthors have all seen the article and agreed to its submission to your journal. 

We believe that our article fits within the scope of your journal due to being a direction response to the work of Ogino, Suzuki, and Sawada (1987), which was published in volume 51 issue 10 of your journal.  Our work entails a mathematical framework by which an entire calcium-carbonate precipitation process can be described.  This descriptions includes the evolution of four polymorphs through a range of physical/chemical phenomena including nucleation, growth, dissolution, coalescence, mixing, and equilibrium chemistry. 

\closing{Thank you for your consideration,}

\end{letter}
\end{document}
